MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-18 MAESTROeX_I/conclusions.tex
more refs
more ferences

\section{Conclusions and Future Work}

science: rotation, solar physics, MHD

algorithm: SDC \cite{dutt2000spectral}, high-order, multi-implicit \cite{bourlioux2003high}.
Consider SDC ideas used for terrestrial combustion \cite{pazner2016high,nonaka2018conservative}

implementation: GPUs.  Forward cite next CASTRO paper with GPU strategy.

>>>>

\section{Conclusions and Future Work}
Our new implementation of the MAESTRO code in the AMReX software framework

Our future scientific investigations include convection in massive rotating stars, \citep{heger2000presupernova}, the convective Urca process in white dwarfs \citep{willcox2016type}, solar physics \citep{wood2018self}, and magnetohydrodynamics \citep{wood2015three,wood2011sun}.

Our future algorithmic enhancements include more accurate and higher-order multiphysics coupling strategies byased on spectral deferred corrections \cite{dutt2000spectral,bourlioux2003high}.
This framework has been successfully used in terrestrial combustion \cite{pazner2016high,nonaka2018conservative}

Our software enhancements will include GPU implementation.
\MarginPar{Forward cite CASTRO paper; add a few sentences on GPU strategy}

### 2019-03-18 MAESTROeX_I/intro.tex
more ferences

We also present new algorithmic methodology that improves upon Paper V in a number of ways.
First, the overall temporal algorithm has been greatly simplified without compromising accuracy.
The key design decision was to replace the predicted evolution of the base state with 
a predictor-corrector approach.  Not only does this greatly simplify the dynamics of the base
state, but this treatment is more amenable to higher-order multiphysics coupling strategies
based on method-of-lines integration.  Second, we now provide additional spatial mapping
procedures that reduces, and in some cases eliminates, mapping error from the one-dimensional
base state to the Cartesian grid state for spherical problems.
Finally, the code has been completely ported to a new software framework suitable for modern manycore supercomputers.
The resulting MAESTROeX is implemented in the C++/F90 AMReX software library.  MAESTROeX uses MPI+OpenMP parallelism
and scales well to over 10,000 MPI processes, with each MPI process supporting tens of threads

The resulting code is publicly available on GitHub at {\url https://github.com/AMReX-Astro/MAESTROeX} and uses the microphysics 
libraries at {\url https://github.com/starkiller-astro/Microphysics} and the AMReX software library for block-structured adaptive mesh refinement
{\url https://github.com/AMReX-Codes/amrex}.

>>>>

We also present new algorithmic methodology that improves upon Paper V in a number of ways.
First, the overall temporal algorithm has been greatly simplified without compromising accuracy.
The key design decision was to replace the predicted evolution of the base state with 
a predictor-corrector approach.  Not only does this greatly simplify the dynamics of the base
state, but this treatment is more amenable to higher-order multiphysics coupling strategies
based on method-of-lines integration.  Second, we now provide additional spatial mapping
procedures that reduces, and in some cases eliminates, mapping error from the one-dimensional
base state to the Cartesian grid state for spherical problems.
Finally, the code has been completely ported to a new software framework suitable for modern manycore supercomputers.
The resulting MAESTROeX is implemented in the C++/F90 AMReX public software library \cite{AMReX}.  
MAESTROeX uses MPI+OpenMP parallelism and scales well to over 10,000 MPI processes, with each MPI process supporting tens of threads
The resulting code is publicly available on GitHub at {\url https://github.com/AMReX-Astro/MAESTROeX} and uses the microphysics 
libraries at {\url https://github.com/starkiller-astro/Microphysics} and the AMReX software library for block-structured adaptive mesh refinement
{\url https://github.com/AMReX-Codes/amrex}.
